### 2021-03-09 README.Rmd
updated docs #25

>>>>

### Confusion matrix

The skater package adapts functionality from the [m-clark/confusion_matrix](https://github.com/m-clark/confusionMatrix) package to create a confusion matrix and statistics with minimal dependencies.

First, take the `kinpairs` data from above and randomly flip ~20% of the true relationship degrees.

```{r}
# Function to randomly flip levels of a factor (at 20%, by default)
randomflip <- function(x, p=.2) ifelse(runif(length(x))<p, sample(unique(x)), x)

# Infer degree (truth/target) using kin2degree, then randomly flip 20% of them
set.seed(42)
kinpairs_inferred <- kinpairs %>% 
  dplyr::mutate(degree_truth=kin2degree(k, max_degree=3)) %>% 
  dplyr::mutate(degree_truth=tidyr::replace_na(degree_truth, "unrelated")) %>% 
  dplyr::mutate(degree_inferred=randomflip(degree_truth))
kinpairs_inferred
```

The `confusion_matrix` function on its own outputs a list with three objects:

1. Calculates accuracy, lower and upper bounds, the guessing rate and p-value of the accuracy vs. the guessing rate. 
2. Calculates by class the following statistics:
  - Sensitivity = A/(A+C)
  - Specificity = D/(B+D)
  - Prevalence = (A+C)/(A+B+C+D)
  - Positive Predictive Value = (sensitivity * prevalence)/((sensitivity*prevalence) + ((1-specificity)*(1-prevalence)))
  - Negative Predictive Value = (specificity * (1-prevalence))/(((1-sensitivity)*prevalence) + ((specificity)*(1-prevalence)))
  - Detection Rate = A/(A+B+C+D)
  - Detection Prevalence = (A+B)/(A+B+C+D)
  - Balanced Accuracy = (sensitivity+specificity)/2
  - Precision = A/(A+B)
  - Recall = A/(A+C)
  - F1 = harmonic mean of precision and recall
  - False Discovery Rate = 1 - Positive Predictive Value
  - False Omission Rate = 1 - Negative Predictive Value
  - False Positive Rate = 1 - Specificity
  - False Negative Rate = 1 - Sensitivity
3. The contingency table object itself.

```{r}
confusion_matrix(prediction = kinpairs_inferred$degree_inferred, 
                 target = kinpairs_inferred$degree_truth)
```

Pluck out just the contingency table:

```{r}
confusion_matrix(prediction = kinpairs_inferred$degree_inferred, 
                 target = kinpairs_inferred$degree_truth) %>% 
  purrr::pluck("Table")
```

Output in tidy (`longer=TRUE`) format, then spread stats by class:

```{r}
confusion_matrix(prediction = kinpairs_inferred$degree_inferred, 
                 target = kinpairs_inferred$degree_truth, 
                 longer = TRUE) %>% 
  purrr::pluck("Other") %>% 
  tidyr::spread(Class, Value) %>% 
  dplyr::relocate(Average, .after=dplyr::last_col()) %>% 
  dplyr::mutate_if(rlang::is_double, signif, 2) %>% 
  knitr::kable()
```
